---
title: "Polynomial Regression"
author: "Bruno Carlin"
date: "29/07/2018"
output:
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
---
# Importing the libraries
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("~/R.Stuff/Krill-Machine-Learning/Machine Learning A-Z Template Folder/Part 2 - Regression/Section 6 - Polynomial Regression/Polynomial Regression"))
```

```{r R Library}
library(reticulate)
library(caTools)
library(tidyverse)
set.seed(123)
```


```{python Pythom Library}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
import os
os.environ['QT_QPA_PLATFORM_PLUGIN_PATH'] = '/Users/Anton/Anaconda3/Library/plugins/platforms'
```


# Python

## Importing the dataset


```{python}
dataset = pd.read_csv('Position_Salaries.csv')
X = dataset.iloc[:, 1:2].values
y = dataset.iloc[:, 2].values
```

## Fitting the Regression Model to the dataset

### Fitting Linear Regression to the dataset

```{python}
from sklearn.linear_model import LinearRegression
lin_reg = LinearRegression()
lin_reg.fit(X, y)
```

### Fitting Polynomial Regression to the dataset

```{python}
from sklearn.preprocessing import PolynomialFeatures
poly_reg = PolynomialFeatures(degree = 4)
X_poly = poly_reg.fit_transform(X)
poly_reg.fit(X_poly, y)
lin_reg_2 = LinearRegression()
lin_reg_2.fit(X_poly, y)
```

## Visualising the Regression Models

### Visualising the Linear Regression results

```{python}
plt.scatter(X, y, color = 'red')
plt.plot(X, lin_reg.predict(X), color = 'blue')
plt.title('Truth or Bluff (Linear Regression)')
plt.xlabel('Position level')
plt.ylabel('Salary')
plt.show()
plt.close()
```

### Visualising the Polynomial Regression results

```{python}
plt.scatter(X, y, color = 'red')
plt.plot(X, lin_reg_2.predict(poly_reg.fit_transform(X)), color = 'blue')
plt.title('Truth or Bluff (Polynomial Regression)')
plt.xlabel('Position level')
plt.ylabel('Salary')
plt.show()
plt.close()
```

### Combined

```{python}
plt.scatter(X, y, color = 'red')
plt.plot(X, lin_reg.predict(X), color = 'blue')
plt.title('Truth or Bluff (Linear Regression)')
plt.xlabel('Position level')
plt.ylabel('Salary')

plt.scatter(X, y, color = 'red')
plt.plot(X, lin_reg_2.predict(poly_reg.fit_transform(X)), color = 'blue')
plt.title('Truth or Bluff (Polynomial Regression)')
plt.xlabel('Position level')
plt.ylabel('Salary')
plt.show()
plt.close()
```

## Visualising the Polynomial Regression results (for higher resolution and smoother curve)

```{python}
X_grid = np.arange(min(X), max(X), 0.1)
X_grid = X_grid.reshape((len(X_grid), 1))
plt.scatter(X, y, color = 'red')
plt.plot(X_grid, lin_reg_2.predict(poly_reg.fit_transform(X_grid)), color = 'blue')
plt.title('Truth or Bluff (Polynomial Regression)')
plt.xlabel('Position level')
plt.ylabel('Salary')
plt.show()
```

## Predicting a new result with Linear Regression

```{python}
lin_reg.predict(6.5)
```

## Predicting a new result with Polynomial Regression

```{python}
lin_reg_2.predict(poly_reg.fit_transform(6.5))
```


# R

## Importing the dataset
```{r}
dataset = read.csv('Position_Salaries.csv')
dataset = dataset[2:3]
```


## Fitting Linear Regression to the dataset

```{r}
lin_reg <- dataset %>% lm(formula = Salary ~.)
```

## Fitting Polynomial Regression to the dataset

```{r}
dataset$Level2 <- dataset$Level^2
dataset$Level3 <- dataset$Level^3
dataset$Level4 <- dataset$Level^4
poly_reg <- dataset %>% lm(formula = Salary ~.)
```

## Visualising the Regression results

### Visualising the Linear Regression results
```{r}
ggplot() +
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(lin_reg, newdata = dataset)),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Linear Regression)') +
  xlab('Level') +
  ylab('Salary')
```

### Visualising the Polynomial Regression results
```{r}
ggplot() +
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(poly_reg, newdata = dataset)),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Polynomial Regression)') +
  xlab('Level') +
  ylab('Salary')
```


###Both
```{r}
ggplot() +
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(lin_reg, newdata = dataset)),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Both Regressions)') +
  xlab('Level') +
  ylab('Salary') +
  
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(poly_reg, newdata = dataset)),
            colour = 'blue')
```

## Visualising the Regression Model results (for higher resolution and smoother curve)
```{r}
x_grid = seq(min(dataset$Level), max(dataset$Level), 0.1)
ggplot() +
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = x_grid, y = predict(poly_reg,
                                        newdata = data.frame(Level = x_grid,
                                                             Level2 = x_grid^2,
                                                             Level3 = x_grid^3,
                                                             Level4 = x_grid^4))),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Polynomial Regression)') +
  xlab('Level') +
  ylab('Salary')
```

## Predicting a new result with Linear Regression

```{r}
predict(lin_reg, data.frame(Level = 6.5))
```

## Predicting a new result with Polynomial Regression

```{r}
predict(poly_reg, data.frame(Level = 6.5,
                             Level2 = 6.5^2,
                             Level3 = 6.5^3,
                             Level4 = 6.5^4))
```

## Predicting a new result with Polynomial Regression(Better? Can`t pipe)

```{r}
poly_reg2 = lm(Salary ~ Level + I(Level^2) + I(Level^3) + I(Level^4), data=dataset)

predict(poly_reg2, data.frame(Level=6.5))
```


