---
title: "Simple.Linear.Regression"
author: "Bruno Carlin"
date: "07/07/2018"
output:
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
---

# Importing the libraries

## R

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("~/TCC/R/Krill-Machine-Learning/Machine Learning A-Z Template Folder/Part 2 - Regression/Section 4 - Simple Linear Regression"))
```

```{r}
library(reticulate)
library(caTools)
set.seed(123)
```


## Python
```{python pYTHON}

import pandas as py
import matplotlib.pyplot as plt
import pandas as pd

``` 

# Importing the dataset

## Python

Requires the dataset to be in the same folder
```{python}
dataset = pd.read_csv('SalaryData.csv')
X = dataset.iloc[:,:-1].values
y = dataset.iloc[:,1].values
```

## R
```{r, echo=FALSE, background= T}
X <- py$X
y <- py$y
dataset = py$dataset

#OR
dataset = read.csv('SalaryData.csv')
```


# Spliting the dataset into the Training set and Test set

## Python

```{python}
from sklearn.model_selection import train_test_split
X_train,X_test,y_train,y_test = train_test_split(
X,y,test_size = 1/3,random_state = 0)
```

## R

###library(caTools)

```{r}
#library(caTools)
set.seed(123)
split = sample.split(dataset[,1], SplitRatio = 2/3)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```




# Feature Scaling

## Python

```{python eval=FALSE, include=FALSE}
from sklearn.preprocessing import StandardScaler
sc_X = StandardScaler()
X_train = sc_X.fit_transform(X_train)
X_test = sc_X.transform(X_test)
```

## R

```{r eval=FALSE, include=FALSE}
 training.set[2:3] = scale(training.set[,2:3])
 test.set[2:3] = scale(test.set[,2:3])
```

# Fitting Simple Linear Regression to the Training set

## Python
```{python}
from sklearn.linear_model import LinearRegression
regressor = LinearRegression()
regressor.fit(X_train, y_train)
```

## R

```{r}
regressor = lm(formula = Salary ~ YearsExperience,
               data = training_set)
```

# Predicting the Test set results

## Python


```{python}
y_pred = regressor.predict(X_test)
```


## R

```{r}
y_pred = predict(regressor, newdata = test_set)
```


# Visualising the Training set results

## Python 
```{python eval=FALSE, include=FALSE}
plt.scatter(X_train, y_train, color = 'red')
plt.plot(X_train, regressor.predict(X_train), color = 'blue')
plt.title('Salary vs Experience (Training set)')
plt.xlabel('Years of Experience')
plt.ylabel('Salary')
plt.show()
```

## R


```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(x = training_set$YearsExperience, y = training_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Training set)') +
  xlab('Years of experience') +
  ylab('Salary')
```

# Visualising the Test set results


## Python


```{python eval=FALSE, include=FALSE}
plt.scatter(X_test, y_test, color = 'red')
plt.plot(X_train, regressor.predict(X_train), color = 'blue')
plt.title('Salary vs Experience (Test set)')
plt.xlabel('Years of Experience')
plt.ylabel('Salary')
plt.show()
```

##  R

```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(x = test_set$YearsExperience, y = test_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Test set)') +
  xlab('Years of experience') +
  ylab('Salary')
```



