---
title: "Multiple Linear Regression"
author: "Bruno Carlin"
date: "09/07/2018"
output:
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
---

# Importing the libraries
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("~/R.Stuff/Krill-Machine-Learning/Machine Learning A-Z Template Folder/Part 2 - Regression/Section 5 - Multiple Linear Regression"))
```

```{r R Library}
library(reticulate)
library(caTools)
set.seed(123)
```


```{python Pythom Library}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```


# Python

## Importing the dataset

```{python}
dataset = pd.read_csv('50_Startups.csv')
X = dataset.iloc[:, :-1].values
y = dataset.iloc[:, 4].values
```


## Encoding categorical data
## Encoding the Independent Variable
```{python}
from sklearn.preprocessing import LabelEncoder, OneHotEncoder
labelencoder_X = LabelEncoder()
X[:, 3] = labelencoder_X.fit_transform(X[:, 3])
onehotencoder = OneHotEncoder(categorical_features = [3])
X = onehotencoder.fit_transform(X).toarray()
# Avoiding the Dummy Variable trap
X = X[:,1:]
```


## Splitting the dataset into the Training set and Test set
```{python}
from sklearn.model_selection import train_test_split
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size = 0.2, random_state = 0)
```

## Fitting Multiple Linear Regression to the Training set

```{python}
from sklearn.linear_model import LinearRegression
regressor = LinearRegression()
regressor.fit(X_train, y_train)
```

## Predicting the Test set results

```{python}
y_pred = regressor.predict(X_test)
```

## Building the optimal model using Backward Elimination

```{python}
import statsmodels.formula.api as sm
X = np.append(arr = np.ones((50,1)).astype(int),values = X ,axis = 1)
X_opt = X[:,[0,1,2,3,4,5]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
X_opt = X[:,[0,3,4,5]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
X_opt = X[:,[0,3,4,5]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
X_opt = X[:,[0,3,5]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
X_opt = X[:, [0, 3]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
X_opt = X[:,[4,5]]
regressor_OLS = sm.OLS(endog = y, exog = X_opt).fit()
regressor_OLS.summary()
```


## Automatic selection


```{python}
import statsmodels.formula.api as sm
def backwardElimination(x, SL):
    numVars = len(x[0])
    temp = np.zeros((50,6)).astype(int)
    for i in range(0, numVars):
        regressor_OLS = sm.OLS(y, x).fit()
        maxVar = max(regressor_OLS.pvalues).astype(float)
        adjR_before = regressor_OLS.rsquared_adj.astype(float)
        if maxVar > SL:
            for j in range(0, numVars - i):
                if (regressor_OLS.pvalues[j].astype(float) == maxVar):
                    temp[:,j] = x[:, j]
                    x = np.delete(x, j, 1)
                    tmp_regressor = sm.OLS(y, x).fit()
                    adjR_after = tmp_regressor.rsquared_adj.astype(float)
                    if (adjR_before >= adjR_after):
                        x_rollback = np.hstack((x, temp[:,[0,j]]))
                        x_rollback = np.delete(x_rollback, j, 1)
                        print (regressor_OLS.summary())
                        return x_rollback
                    else:
                        continue
    regressor_OLS.summary()
    return x
 
SL = 0.05
X_opt = X[:, [0, 1, 2, 3, 4, 5]]
X_Modeled = backwardElimination(X_opt, SL)
```

# R

## Importing the dataset

```{r}
dataset = read.csv('50_Startups.csv')
```

## Encoding categorical data
```{r}
dataset$State = factor(
  dataset$State,
  levels = c('New York', 'California', 'Florida'),
  labels = c(1, 2, 3)
)
```


## Splitting the dataset into the Training set and Test set

```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```


## Fittiing Multiple Linear Regression to the Training set

```{r}
regressor <- lm(formula = Profit ~ ., data = training_set)
summary(regressor)
```


## Predicting the Test set Results

```{r}
y_pred <- predict(regressor, newdata = test_set)
#or
library(tidyverse)
Y_Pred <- regressor %>% predict(test_set)

#Even better
Y_Optimal_Pred <- regressor %>% step() %>%predict(test_set)

#Also works

backwardElimination <- function(x, sl) {
  numVars = length(x)
  for (i in c(1:numVars)){
    regressor = lm(formula = Profit ~ ., data = x)
    maxVar = max(coef(summary(regressor))[c(2:numVars), "Pr(>|t|)"])
    if (maxVar > sl){
      j = which(coef(summary(regressor))[c(2:numVars), "Pr(>|t|)"] == maxVar)
      x = x[, -j]
    }
    numVars = numVars - 1
  }
  return(summary(regressor))
}

SL = 0.05
dataset = dataset[, c(1,2,3,4,5)]
backwardElimination(training_set, SL)
```

